---
title: "R interface chatGPT"
---

## Setup

Clone the repository:

```sh
git clone 
```

Create a file called `.env.R` that stores your chatGPT PAT in an ojbect called `API_KEY` , so e.g.

```{r}
#| eval: false
API_KEY <- "sk-XXXXXXXXXXX"
```

After that, source the functions in `main.R` and the environment file:

```{r}
source("main.R")
source(".env.R")
```

## ChatGPT with R

Now you can play around with a simple chatGPT interface:

```{r}
chatGPT("Tell me a joke about a bioinformatician") |> cat()
```

You can also change the system prompt, i.e. the background style/information of the responder:

```{r}
chatGPT(user_prompt = "Are fungi eukaryotes?",
        system_prompt = "You are a helpful assistant, that's also a cool surfer dude") |> cat()
```

If you're asking for R code, this can be extracted and run on the fly

```{r}
string <- chatGPT("Generate a scatterplot with ggplot2 where the size of the points is defined by a column called 'size', and the color is defined by a column called 'color'")

extract_code(string) |> sapply(cat)

extract_code(string)[[1]] |> parse(text = _) |> eval()
```

Also nice is that it can create shiny apps:

```{r}
string <- chatGPT("Create a r shiny app that creates a histogram of set of random numbers. Let the user choose the mean, standard deviation and number of observations")

extract_code(string) |> sapply(cat)
```
